Fast, Scalable Phrase-Based SMT Decoding

### 2016-01-28 acl.2016/acl2016.tex
acl paper

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{times}
\usepackage{latexsym}

@@

Over 30\% of the Moses decoder running time is spent on memory management and this increases when more threads are used, Table~\ref{tab:optimizing-memory}. By contrast, our decoder spends ???\% on memory management.
\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& 1 thread	& 30 threads \\ \hline
Moses  		& ???\% 	& ???\% \\
Our work 	& ???\% 	& ???\% \\ \hline
\end{tabular}
\end{center}
\caption{\%age decoding time managing memory}
\label{tab:optimizing-memory}
\end{table}

A potential disadvantage of using memory pool is that the decoder will use more memory, however, Table~\ref{tab:memory-usage} shows that peak memory consumption are comparable.
\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& 1 thread	& 30 threads \\ \hline
Moses  		& ???	 	& ??? \\
Our work 	& ??? 		& ??? \\ \hline
\end{tabular}
\end{center}
\caption{Peak Memory Usage in GB}
\label{tab:memory-usage}
\end{table}

@@

However, we also note that distortion limit which constrains hypothesis extension is dependent on the hypothesis' coverage vector \emph{and} the end position of most recent source word that has been translated. Therefore, if the hypotheses are separated by coverage vector \emph{and} end position, the distortion limit constraint can be moved to an outer loop, potentially speeding up decoding.

>>>>

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{times}
\usepackage{latexsym}
\usepackage{algorithmic}

@@

Over 30\% of the Moses decoder running time is spent on memory management and this increases when more threads are used, Table~\ref{tab:optimizing-memory}. By contrast, our decoder spends ???\% on memory management.
\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& 1 thread	& 32 threads \\ \hline
Moses  		& ???\% 	& ???\% \\
Our work 	& ???\% 	& ???\% \\ \hline
\end{tabular}
\end{center}
\caption{\%age decoding time managing memory}
\label{tab:optimizing-memory}
\end{table}

A potential disadvantage of using memory pool is that the decoder will use more memory, however, Table~\ref{tab:memory-usage} shows that peak memory consumption are comparable.
\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& 1 thread	& 32 threads \\ \hline
Moses  		& ???	 	& ??? \\
Our work 	& ??? 		& ??? \\ \hline
\end{tabular}
\end{center}
\caption{Peak Memory Usage in GB}
\label{tab:memory-usage}
\end{table}

@@

However, we also note that distortion limit which constrains hypothesis extension is dependent on the hypothesis' coverage vector \emph{and} the end position of most recent source word that has been translated. Using a cardinality-based stack, the distortion limit must be checked for every instance, Figure~\ref{algo:Hypothesis Expansion with Unsorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\STATE insert empty hypothesis into $stack_0$
\FOR{$i = 0$ to $|s|-1$} 
  \STATE prune $stack_i$
  \FORALL{ hypothesis in $stack_i$} 
    \FORALL{ translation options}
       \IF {hypothesis and translation option are compatible}
         \STATE expand hypothesis with translation option $\rightarrow$ new hypothesis
         \STATE coverage of  new hypothesis $\rightarrow C$
         \STATE insert new hypothesis $\rightarrow stack_{|C|}$
         \STATE recombine new hypothesis if possible
         \STATE prune $stack_{|C|}$ if necessary
       \ENDIF
    \ENDFOR % { translation options}
  \ENDFOR % { hypothesis in $stack_i$} 
\ENDFOR% {$i = 0$ to $|s|-1$} 
\RETURN highest scoring hypothesis in $stack_{|s|}$
\end{algorithmic}
\caption{Hypothesis Expansion with Unsorted Stack}
\label{algo:Hypothesis Expansion with Unsorted Stack}
\end{figure}

Therefore, if the hypotheses are separated by coverage vector and end position, the distortion limit constraint can be moved to an outer loop, potentially speeding up decoding.
